A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
stage 4 writing

\subsection{FFDH (First-Fit Decreasing-Height)}
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput

>>>>

\subsection{FFDH (First-Fit Decreasing-Height)}

\section{Steinberg's Algorithm}
\par In this section we introduce a more advanced approximation algorithm designed by \cite{steinberg1997strip}. Instead of heuristically packing every rectangle and output the height as result, Steinberg gave a more specific bound on the height $\hat{h}$ of the bin, with which a valid packing can be found easily. This is guaranteed by the following theorem.
\paragraph{Steinberg's Theorem} If the following inequalities hold
\begin{eqnarray}
	a_M &= \max_{1\leq i\leq n} a_i \\
	b_M &= \max_{1\leq i\leq n} b_i \\
\end{eqnarray}
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput
